---
title: "workflow"
author: "Josh Erickson"
date: "11/8/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")),fig.width = 10, fig.height = 5,
                      warning = FALSE, message = FALSE, error = FALSE)
library(patchwork)
library(tidyverse)
library(GGally)
library(car)
library(broom)
library(sf)
library(performance)
library(resourceviz)
library(caret)
library(CAST)
library(glmnet)
thematic::thematic_on(font = 'Montserrat')
source('functions.R')

fish_stuff <- read_csv('pat_fish.csv') %>% janitor::clean_names()

fish_stuff_ts <- read_csv('pat_fish.csv') %>% janitor::clean_names()

fish_stuff_ts <- fish_stuff_ts %>% mutate(stream_id = str_remove_all(stream_id, '-[^-]+$'))

fish_stuff <- fish_stuff %>% mutate(stream_id = str_remove_all(stream_id, '-[^-]+$'))

fish_stuff <- fish_stuff %>% 
  group_by(stream_segment) %>% 
  mutate(across(mean_width_ft:psd150mm, ~mean(.x, na.rm = TRUE), .names = 'mean_{.col}')) %>% ungroup()

fish_stuff <- fish_stuff %>% group_by(stream_id) %>% slice(n=1) %>% ungroup()
```


## Finding/Exploring/Selecting Covariates

```{r}
fish_stuff %>% count(stream)
fish_stuff %>% count(stream_id)

fish_stuff %>% skimr::skim()

fish_stuff %>% filter(!is.na(density_fish_m2)) %>% 
  select(-c('q_cfs', 'fish_1000', 'infs_lwd_mile', 'fish_species', 'size',)) %>% na.omit() %>% 
  skimr::skim()

fish_stuff <- fish_stuff %>% filter(!is.na(density_fish_m2)) %>%
  select(-c('q_cfs', 'fish_1000', 'infs_lwd_mile',
            'x19', 'fish_species', 'size')) %>% na.omit() %>% 
  group_by(stream_id) %>% mutate(mean_dens = mean(density_fish_m2)) %>% ungroup()

mean_dens_cor <- cortest_cols(fish_stuff, density_fish_m2, c(mean_width_ft:mean_residual_pool_depth_ft,psd150mm))


variables_to_check_dens <- mean_dens_cor %>% 
  filter(pvalue <= 0.05)

#Now visualise and go from there


## check bank angle selections
ggpairs(fish_stuff %>% dplyr::select(density_fish_m2,mean_width_ft:mean_residual_pool_depth_ft, psd150mm),upper = list(continuous = wrap("cor", size = 3)),
        lower = list(continuous = wrap("smooth", method = "lm", se = F,
                                               alpha = 0.6))) +
  custom_theme() + labs()

fish_stuff %>% 
  ggplot(aes(pools_mile, density_fish_m2, color = size)) + 
  geom_point(size = 3) +
  custom_theme()
resourceviz::cairo_view()

fish_stuff %>% 
  ggplot(aes(pools_mile, fish_1000, color = mean_width_ft)) + 
  geom_point(size = 5) +
  geom_smooth(method = 'lm', se = F) +
  Add_R2() + 
  scale_color_gradientn(colors = hcl.colors(n = 11, 'Zissou1')) + 
  custom_theme()

```

Looks like `fac_taudem_17all_int`, `us_precip_1981_2010_cpg_all`, `clay_100_cpg_all`, `slope_percent_int_cpg_all`, `swe_avg_0301_cpg_all` and `us_tmax_1981_2010_int_cpg_all` for `mean_bf` and
`fac_taudem_17all_int`, `ave_basin_elev`, `silt_100_cpg_all`, `streamslope_percent_int_cpg_all` and `twi_100_int_cpg_all` for `mean_bank_an` we got `ave_ann_cwd`, `fac_taudem_17all_int`, `us_precip_1981_2010_cpg_all`, `clay_100_cpg_all`, `slope_percent_int_cpg_all`, `swe_avg_0301_cpg_all` and `twi_100_int_cpg_all`. These have
decent $r$ values and also make sense causally so we'll add them to the
model.

## Check Assumptions

Since we are using linear regression (LR) we need to make sure our
models follow LR assumptions; must be linear, multicollinearity, iid,
homoscedastic and normality of residuals. In addition, we need to check
assumptions for ANCOVA; homogeneity of slopes and independence between
iv and covariate(s). We'll start with linearity followed by
multicollinearity and then run the models so we can finish the tests.

### Linearity

We'll take a look at the dv's and the associated covariates to see if
the are linear. Just change variables accordingly. 

```{r}
#mean bf
# just play with function and take notes....
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_bf')
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_bf', log_x = T)
linear_plot(fish_stuff, 'clay_100_cpg_all', 'mean_bf', log_x = T, log_y = T)
linear_plot(fish_stuff, 'us_tmax_1981_2010_int_cpg_all', 'mean_bf', iv = 'mgmt', log_x = T, log_y = T)

#now to mean bank angle
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_bank_an')
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_bank_an', log_x = T)
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_bank_an', log_x = T, log_y = T)
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_bank_an', iv = 'mgmt', log_x = T, log_y = T)


# W/D
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_wd_2009')
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_wd_2009', log_x = T)
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_wd_2009', log_x = T, log_y = T)
linear_plot(fish_stuff, 'fac_taudem_17all_int', 'mean_wd_2009', iv = 'mgmt', log_x = T, log_y = T)
```

## Collinearity  

```{r}

bf_var_collinearity <- collinearity(fish_stuff, c('fac_taudem_17all_int','us_precip_1981_2010_cpg_all',
                                                              'us_tmax_1981_2010_int_cpg_all', 'swe_avg_0301_cpg_all',
                                                              'clay_100_cpg_all', 'slope_percent_int_cpg_all'))
ba_var_collinearity <- collinearity(fish_stuff, c('fac_taudem_17all_int','streamslope_percent_int_cpg_all',
                                                              'ave_basin_elev', 'twi_100_int_cpg_all', 'silt_100_cpg_all'))
wd_var_collinearity <- collinearity(fish_stuff, c('fac_taudem_17all_int','us_precip_1981_2010_cpg_all', 'ave_ann_cwd',
                                                              'swe_avg_0301_cpg_all', 'clay_100_cpg_all', 'slope_percent_int_cpg_all',
                                                              'twi_100_int_cpg_all'))
filter_collinearity(bf_var_collinearity)
filter_collinearity(ba_var_collinearity)
filter_collinearity(wd_var_collinearity)

#all passed
```



## Multicollinearity

We'll use the vif() (variance inflation factor) to check and make sure
we don't have any multicollinearity.

```{r}

multcollinearity_bf <- multi_collin(fish_stuff, 'bf')
multcollinearity_ba <- multi_collin(fish_stuff, 'ba')
multcollinearity_wd <- multi_collin(fish_stuff, 'wd')

multcollinearity_bf
multcollinearity_ba
multcollinearity_wd

#all passed using GVIF after accounting for df (e.g. GVIF^(1/(2*Df)))
```

## iid

Here we'll lump iid and independence between iv and covariate(s). We are
assuming iid since all the observations are independent of each other
and are far enough away; identically distributed is mostly followed
since the observations are 'response' reaches (less than 4% gradient)
but may have different hydrological regimes, i.e. rain-on-snow vs
snowmelt. The iv is not dependent on the covariates since the covariates
are not a function of the iv, i.e. precipitation doesn't care if it's a
managed area or reference; it just happens.

## Models

We'll run the models for ANCOVA below for both dv's. We want the most parsimonous model so we'll use a mixture model (ridge and lasso aka elastic-net) to gain information about the simplest model; managing under-over fitting.

```{r}

lasso_model_bf <- feature_selection(fish_stuff, 'bf')
plot(lasso_model_bf)
var_imp_bf <- varImp(lasso_model_bf$finalModel, lasso_model_bf$bestTune$lambda)
coef(lasso_model_bf$finalModel, lasso_model_bf$bestTune$lambda)
plot(lasso_model_bf$finalModel, label = T)
plot(lasso_model_bf$finalModel, label = T, xvar = c('lambda'))

lasso_model_ba <- feature_selection(fish_stuff, 'ba')
plot(lasso_model_ba)
var_imp_ba <- varImp(lasso_model_ba$finalModel, lasso_model_ba$bestTune$lambda)
coef(lasso_model_ba$finalModel, lasso_model_ba$bestTune$lambda)
plot(lasso_model_bf$finalModel, label = T)
plot(lasso_model_bf$finalModel, label = T, xvar = c('lambda'))

lasso_model_wd <- feature_selection(fish_stuff, 'wd')
plot(lasso_model_wd)
var_imp_wd <- varImp(lasso_model_wd$finalModel, lasso_model_wd$bestTune$lambda)
coef(lasso_model_wd$finalModel, lasso_model_wd$bestTune$lambda)
plot(lasso_model_bf$finalModel, label = T)
plot(lasso_model_bf$finalModel, label = T, xvar = c('lambda'))

```

## Residual assumptions

Now that we have the models we can check the residual assumptions;
homogeneity of variance and normally distributed.

```{r}

bf_results <- check_if_normal_hetero('fish_stuff', 'bf', var_imp = var_imp_bf)
#mean_bf
#not normal
#not hetereoscedastic

ba_results <- check_if_normal_hetero('fish_stuff', 'ba', var_imp = var_imp_ba)
#mean_bank_an
#normal
# not hetereoscedastic 

wd_results <- check_if_normal_hetero('fish_stuff', 'wd', var_imp = var_imp_wd)
#width/depth
#normal
#not hetereoscedastic 
```

Let's look at the `mod_bf` model and see what's going on.

```{r}
qqPlot(mod_bf)
qqPlot(mod_bank)
qqPlot(mod_wd)

plot(mod_bank)
plot(mod_bf)
plot(mod_wd)
```

#Normality and variance checks

Let's see if adding weights will help
```{r}
#now let's do the qqPlot() without these

mod_bf_filt <- lm(log(mean_bf)~log(fac_taudem_17all_int)+
               log(us_precip_1981_2010_cpg_all)+
               log(us_tmax_1981_2010_int_cpg_all) +
               log(slope_percent_int_cpg_all) + 
               MAP_UNIT_N +
               mgmt, data = fish_stuff)

qqPlot(mod_bf_filt)
# looks like 75 and 193
wt <- 1 / lm(abs(mod_bf_filt$residuals) ~ mod_bf_filt$fitted.values)$fitted.values^2
mod_bf_filt <- lm(log(mean_bf)~log(fac_taudem_17all_int)+
               log(us_precip_1981_2010_cpg_all)+
               log(us_tmax_1981_2010_int_cpg_all) +
               log(slope_percent_int_cpg_all) + 
               MAP_UNIT_N +
               mgmt, data = fish_stuff[-c(75,193), ], weights = wt[-c(75,193)])

### Now to bank angle section

mod_ba_filt <- lm(log(mean_bank_an)~log(fac_taudem_17all_int)+
                 log(ave_basin_elev)+
                 log(twi_100_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, 
                 data = fish_stuff)

#don't square the weighted residuals
wt_ba <- 1 / lm(abs(mod_ba_filt$residuals) ~ mod_ba_filt$fitted.values)$fitted.values
qqPlot(mod_ba_filt)
#leave vars in place
mod_ba_filt <- lm(log(mean_bank_an)~log(fac_taudem_17all_int)+
                 log(ave_basin_elev)+
                 log(twi_100_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, 
                 data = fish_stuff,
                 weights = wt_ba)

### Now to width/depth section

mod_wd_filt <- lm(log(mean_wd_2009)~log(fac_taudem_17all_int)+
                 log(us_precip_1981_2010_cpg_all) +
                 log(slope_percent_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, data = fish_stuff)

#don't square the weighted residuals
wt_wd <- 1 / lm(abs(mod_ba_filt$residuals) ~ mod_ba_filt$fitted.values)$fitted.values
qqPlot(mod_wd_filt)
#leave vars in place
mod_wd_filt <- lm(log(mean_wd_2009)~log(fac_taudem_17all_int)+
                 log(us_precip_1981_2010_cpg_all)+
                 log(slope_percent_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, data = fish_stuff,
                 weights = wt_wd)

```
Now we need to see if the regression lines are homogeneous.

## Homogeneity of regression slopes assumption

If the covariate and iv interaction are significant then we have
violated the assumption.

```{r}
### bankfull section

mod_bf_precip <- lm(log(mean_bf)~mgmt*log(us_precip_1981_2010_cpg_all), data = fish_stuff[-c(75,193), ], weights = wt[-c(75,193)])
summary(mod_bf_precip)
#passed

mod_bf_shed <- lm(log(mean_bf)~mgmt*log(fac_taudem_17all_int), data = fish_stuff[-c(75,193), ], weights = wt[-c(75,193)])
summary(mod_bf_shed)
#passed 

mod_bf_slope <- lm(log(mean_bf)~mgmt*log(slope_percent_int_cpg_all), data = fish_stuff[-c(75,193), ], weights = wt[-c(75,193)])
summary(mod_bf_slope)
#passed 

mod_bf_temp <- lm(log(mean_bf)~mgmt*log(us_tmax_1981_2010_int_cpg_all), data = fish_stuff[-c(75,193), ], weights = wt[-c(75,193)])
summary(mod_bf_temp)
#passed 


### bank angle

mod_ba_elev <- lm(log(mean_bank_an)~mgmt*log(ave_basin_elev), data = fish_stuff, weights = wt_ba)
summary(mod_ba_elev)
#passed

mod_ba_twi <- lm(log(mean_bank_an)~mgmt*log(twi_100_int_cpg_all), data = fish_stuff, weights = wt_ba)
summary(mod_ba_twi)

#passed
mod_ba_shed <- lm(log(mean_bank_an)~mgmt*log(fac_taudem_17all_int), data = fish_stuff, weights = wt_ba)
summary(mod_ba_shed)
#passed

mod_ba_silt<- lm(log(mean_bank_an)~mgmt*log(silt_100_cpg_all), data = fish_stuff, weights = wt_ba)
summary(mod_ba_silt)
#failed

#### wd section

mod_wd_cwd <- lm(log(mean_wd_2009)~mgmt*log(ave_ann_cwd), data = fish_stuff, weights = wt_wd)
summary(mod_wd_cwd)
#passed

mod_wd_shed <- lm(log(mean_wd_2009)~mgmt*log(fac_taudem_17all_int), data = fish_stuff, weights = wt_wd)
summary(mod_wd_shed)
#passed 

mod_wd_slope <- lm(log(mean_wd_2009)~mgmt*log(slope_percent_int_cpg_all), data = fish_stuff, weights = wt_wd)
summary(mod_wd_slope)
#passed

mod_wd_precip <- lm(log(mean_wd_2009)~mgmt*log(us_precip_1981_2010_cpg_all), data = fish_stuff, weights = wt_wd)
summary(mod_wd_precip)
#passed 


```



Now check the assumptions of the model.

```{r}

## bankfull width
check_normality(mod_bf_filt)
#normal

check_heteroscedasticity(mod_bf_filt)
#homoscedastic

## bank angle
check_normality(mod_ba_filt)
#normal

check_heteroscedasticity(mod_ba_filt)
#homoscedastic

## wd
check_normality(mod_wd_filt)
#normal

check_heteroscedasticity(mod_wd_filt)
#homoscedastic



```


## Run the final models

```{r}
#for mean_bf filter out high residuals
mod_bf_filt <- lm(log(mean_bf)~log(fac_taudem_17all_int)+
               log(us_precip_1981_2010_cpg_all)+
               log(us_tmax_1981_2010_int_cpg_all) +
               log(slope_percent_int_cpg_all) + 
               MAP_UNIT_N +
               mgmt, data = fish_stuff[-c(75,193), ], weights = wt[-c(75,193)])

Anova(mod_bf_filt, type = 'III')
summary(mod_bf_filt)
#for mean_bf WITHOUT filtering high residuals
mod_bf <- lm(log(mean_bf)~log(fac_taudem_17all_int)+
               log(us_precip_1981_2010_cpg_all)+
               log(us_tmax_1981_2010_int_cpg_all) +
               log(slope_percent_int_cpg_all) + 
               MAP_UNIT_N +
                 mgmt, data = fish_stuff)
car::Anova(mod_bf, type = 'III')
library(gtsummary)
library(gt)

la <- list(`log(fac_taudem_17all_int)`~"log(FA Catchment Area)",
               `log(us_precip_1981_2010_cpg_all)`~"log(FA Average Annual Precipitation)",
               `log(us_tmax_1981_2010_int_cpg_all)`~"log(FA Temperature Max)",
               `log(slope_percent_int_cpg_all)`~"log(FA Basin Slope %)",
               MAP_UNIT_N~"Blocking Factor",
               mgmt~"Indpendent Variable")

tb_bf_filt <- tbl_regression(mod_bf_filt, label = la, 
    pvalue_fun = ~style_pvalue(.x, digits = 2),
    intercept = TRUE)%>% 
  add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  add_glance_table(include = c('r.squared', 
                                     'adj.r.squared',
                                     'df', 'AIC', 'BIC')) %>% 
  italicize_levels()

tb_bf <- tbl_regression(mod_bf, label = la, 
    pvalue_fun = ~style_pvalue(.x, digits = 2),
    intercept = TRUE)%>% 
  add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  add_glance_table(include = c('r.squared', 
                                     'adj.r.squared',
                                     'df', 'AIC', 'BIC')) %>% 
  italicize_levels()


#for mean bank angle
mod_bank <- lm(log(mean_bank_an)~log(fac_taudem_17all_int)+
                 log(ave_basin_elev)+
                 log(twi_100_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, 
                 data = fish_stuff)
mod_ba_filt <- lm(log(mean_bank_an)~log(fac_taudem_17all_int)+
                 log(ave_basin_elev)+
                 log(twi_100_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, 
                 data = fish_stuff,
                 weights = wt_ba)

la_ba <- list(`log(fac_taudem_17all_int)`~"log(FA Catchment Area)",
               `log(ave_basin_elev)`~"log(Mean Basin Elevation)",
               `log(twi_100_int_cpg_all)`~"log(FA TWI)",
               MAP_UNIT_N~"Blocking Factor",
               mgmt~"Indpendent Variable")

tb_ba_filt <- tbl_regression(mod_ba_filt, label = la_ba, 
    pvalue_fun = ~style_pvalue(.x, digits = 2),
    intercept = T)%>% 
  add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  add_glance_table(include = c('r.squared', 
                                     'adj.r.squared',
                                     'df', 'AIC', 'BIC')) %>% 
  italicize_levels()

tb_ba <- tbl_regression(mod_bank, label = la_ba, 
    pvalue_fun = ~style_pvalue(.x, digits = 2),
    intercept = T)%>% 
  add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  add_glance_table(include = c('r.squared', 
                                     'adj.r.squared',
                                     'df', 'AIC', 'BIC')) %>% 
  italicize_levels()

### wd section 
mod_wd <- lm(log(mean_wd_2009)~log(fac_taudem_17all_int)+
                 log(us_precip_1981_2010_cpg_all)+
                 log(slope_percent_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, data = fish_stuff)

#leave vars in place
mod_wd_filt <- lm(log(mean_wd_2009)~log(fac_taudem_17all_int)+
                 log(us_precip_1981_2010_cpg_all)+
                 log(slope_percent_int_cpg_all) +
                 MAP_UNIT_N +
                 mgmt, data = fish_stuff,
                 weights = wt_wd)
la <- list(`log(fac_taudem_17all_int)`~"log(FA Catchment Area)",
               `log(us_precip_1981_2010_cpg_all)`~"log(FA Average Annual Precipitation)",
               `log(slope_percent_int_cpg_all)`~"log(FA Basin Slope %)",
               MAP_UNIT_N~"Blocking Factor",
               mgmt~"Indpendent Variable")

tb_wd_filt <- tbl_regression(mod_wd_filt, label = la, 
    pvalue_fun = ~style_pvalue(.x, digits = 2),
    intercept = T)%>% 
  add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  add_glance_table(include = c('r.squared', 
                                     'adj.r.squared',
                                     'df', 'AIC', 'BIC')) %>% 
  italicize_levels()

tb_wd <- tbl_regression(mod_wd, label = la, 
    pvalue_fun = ~style_pvalue(.x, digits = 2),
    intercept = T)%>% 
  add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  add_glance_table(include = c('r.squared', 
                                     'adj.r.squared',
                                     'df', 'AIC', 'BIC')) %>% 
  italicize_levels()




# merge tables 
tbl_merge_ex1 <-
  tbl_merge(
    tbls = list(tb_bf, tb_bf_filt,
                tb_wd, tb_wd_filt,
                tb_ba, tb_ba_filt),
    tab_spanner = c("**Mean Bankfull Width**","**Adjusted Bankfull**",
                    "**Mean Width/Depth**", "**Adjusted Width/Depth**",
                    "**Mean Bank Angle**", "**Adjusted Bank Angle**")
    )


tab <- tbl_merge_ex1 %>% 
  as_gt() %>% 
   tab_header(
    title = "Model Results for multivariate ANCOVA"
  ) %>% 
  opt_align_table_header(align = 'left') %>% 
  tab_footnote(footnote = 'sites not included in the model: Calf Creek (Ref) and S.F. Pilgrim (Man)',
               locations = cells_column_spanners('**Adjusted Bankfull**'))%>% 
  tab_footnote(footnote = 'weighted methods applied',
               locations = cells_column_spanners(c('**Adjusted Bankfull**',
                                                   "**Adjusted Bank Angle**",
                                                   "**Adjusted Width/Depth**"))) %>% 
  tab_footnote(footnote = 'Only data from 2009-present',
               locations = cells_column_spanners(c("**Mean Width/Depth**",
                                                   "**Adjusted Width/Depth**")))

tab

tab %>% gtsave('ancova_results_final.png', expand = 50)
```

## Now we'll look at estimated marginal means

We now need to look at the estimated marginal means (emm) along with the
confidence intervals to see how the groups compare.

```{r}
library(emmeans)
library(car)
library(gt)

mgmt_diff <- emmeans::emmeans(mod_bf_filt, specs = 'mgmt')

mgmt_diff <- plot(mgmt_diff) + custom_theme()

mgmt_diff_gg <- as.data.frame(mgmt_diff$data) %>% tibble()

#get mean difference between groups

mgmt_diff_gg %>% select(-pri.fac, -lcl, -ucl, -df) %>% 
                        mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>%
                        mutate(across(is.numeric, round, 5)) %>% 
                        rename(IV = 'mgmt',
                               `EMM` = 'the.emmean',
                               `Standard Error` = 'SE',
                               `Lower 95% CL` = 'lower.CL',
                               `Upper 95% CL` = 'upper.CL')  %>% 
                        mutate(DV = 'Mean Bankfull Width') %>% 
                        gt() %>%
  tab_header(
    title = "Estimated Marginal Mean (EMM) Results"
  )


m1 <- mgmt_diff_gg %>% mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  geom_errorbar(aes(the.emmean, mgmt, color=mgmt,xmin = lower.CL, xmax = upper.CL), size = 2,
                show.legend = F, width = 0.5) +
  geom_point(aes(the.emmean, mgmt), size = 5) +
  custom_theme(font_size = 15) + 
  labs(x = 'Predicted Mean Bankfull Width (m)', y = '')

m1 

mgmtArea_diff <- emmeans::emmeans(mod_bf_filt, specs = 'mgmt', by = 'MAP_UNIT_N')
mgmt_diff_area <- plot(mgmtArea_diff) + custom_theme()

mgmt_diff_gg_area <- as.data.frame(mgmt_diff_area$data) %>% tibble()

m2 <- mgmt_diff_gg_area %>% mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  geom_errorbar(aes(the.emmean, mgmt, color=mgmt,xmin = lower.CL, xmax = upper.CL),
                width = 0.5, 
                size = 2,
                show.legend = F) +
  geom_point(aes(the.emmean, mgmt), size = 2) +
  custom_theme(font_size = 15) + 
  labs(x = 'Predicted Mean Bankfull Width (m)', y = '') +
  theme(axis.text.y = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.y = element_blank()) +
  facet_wrap(~MAP_UNIT_N)

library(patchwork)

mgmt_diff_filt_ba <- emmeans::emmeans(mod_ba_filt, specs = 'mgmt')

mgmt_diff_filt_ba <- plot(mgmt_diff_filt_ba) + custom_theme()

mgmt_diff_gg_filt_ba <- as.data.frame(mgmt_diff_filt_ba$data) %>% tibble()

#get mean difference between groups

mgmt_diff_gg_filt_ba %>% select(-pri.fac, -lcl, -ucl, -df) %>% 
                        mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>%
                        mutate(across(is.numeric, round, 5)) %>% 
                        rename(IV = 'mgmt',
                               `EMM` = 'the.emmean',
                               `Standard Error` = 'SE',
                               `Lower 95% CL` = 'lower.CL',
                               `Upper 95% CL` = 'upper.CL')  %>% 
                        gt() %>%
  tab_header(
    title = "Estimated Marginal Mean (EMM) Results"
  )


m3 <- mgmt_diff_gg_filt_ba %>% mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  geom_errorbar(aes(the.emmean, mgmt, color=mgmt,xmin = lower.CL, xmax = upper.CL), size = 2,
                show.legend = F, width = 0.5) +
  geom_point(aes(the.emmean, mgmt), size = 5) +
  custom_theme(font_size = 15) + 
  labs(x = 'Predicted Mean Bank Angle (deg)', y = '')

m3 

mgmtArea_diff_ba <- emmeans::emmeans(mod_ba_filt, specs = 'mgmt', by = 'MAP_UNIT_N')
mgmtArea_diff_ba <- plot(mgmtArea_diff_ba) + custom_theme()

mgmt_diff_gg_area_ba <- as.data.frame(mgmtArea_diff_ba$data) %>% tibble()

m4 <- mgmt_diff_gg_area_ba %>% mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  geom_errorbar(aes(the.emmean, mgmt, color=mgmt,xmin = lower.CL, xmax = upper.CL),
                width = 0.5, 
                size = 2,
                show.legend = F) +
  geom_point(aes(the.emmean, mgmt), size = 2) +
  custom_theme(font_size = 15) + 
  labs(x = 'Predicted Mean Bank Angle (deg)', y = '') +
  theme(axis.text.y = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.y = element_blank()) +
  facet_wrap(~MAP_UNIT_N)

m4
### wd

mgmt_diff_filt_wd <- emmeans::emmeans(mod_wd_filt, specs = 'mgmt')

mgmt_diff_filt_wd <- plot(mgmt_diff_filt_wd) + custom_theme()

mgmt_diff_gg_wd <- as.data.frame(mgmt_diff_filt_wd$data) %>% tibble()

#get mean difference between groups

t1 <- mgmt_diff_gg_wd %>% select(-pri.fac, -lcl, -ucl, -df) %>% 
                        mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>%
                        mutate(across(is.numeric, round, 5)) %>% 
                        rename(IV = 'mgmt',
                               `EMM` = 'the.emmean',
                               `Standard Error` = 'SE',
                               `Lower 95% CL` = 'lower.CL',
                               `Upper 95% CL` = 'upper.CL')  %>% 
                        gt() %>%
  tab_header(
    title = "Estimated Marginal Mean (EMM) Results"
  )


m5 <- mgmt_diff_gg_wd %>% mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  geom_errorbar(aes(the.emmean, mgmt, color=mgmt,xmin = lower.CL, xmax = upper.CL), size = 2,
                show.legend = F, width = 0.5) +
  geom_point(aes(the.emmean, mgmt), size = 5) +
  custom_theme(font_size = 15) + 
  labs(x = 'Predicted Mean Width/Depth', y = '')

m5 

mgmtArea_diff_wd <- emmeans::emmeans(mod_wd_filt, specs = 'mgmt', by = 'MAP_UNIT_N')
mgmtArea_diff_wd <- plot(mgmtArea_diff_wd) + custom_theme()

mgmt_diff_gg_area_wd <- as.data.frame(mgmtArea_diff_wd$data) %>% tibble()

m6 <- mgmt_diff_gg_area_wd %>% mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  geom_errorbar(aes(the.emmean, mgmt, color=mgmt,xmin = lower.CL, xmax = upper.CL),
                width = 0.5, 
                size = 2,
                show.legend = F) +
  geom_point(aes(the.emmean, mgmt), size = 2) +
  custom_theme(font_size = 15) + 
  labs(x = 'Predicted Width/Depth', y = '') +
  theme(axis.text.y = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.y = element_blank()) +
  facet_wrap(~MAP_UNIT_N)

m6

((m1 + labs(title = 'a)'))|(m2 + labs(title = 'b)')))/
((m3 + labs(title = 'c)'))|(m4 + labs(title = 'd)')))/
((m5 + labs(title = 'e)'))|(m6 + labs(title = 'f)')))



mgmt_diff_gg %>%
  mutate(DV = 'Mean Bankfull Width') %>%  
  bind_rows(#mgmt_diff_gg_area %>% mutate(DV = 'Mean Bankfull Width'),
            mgmt_diff_gg_filt_ba %>% mutate(DV = 'Mean Bank Angle'),
            #mgmt_diff_gg_area_ba %>% mutate(DV = 'Mean Bank Angle'),
            mgmt_diff_gg_wd %>% mutate(DV = 'Mean Width/Depth'),
           # mgmt_diff_gg_area_wd %>% mutate(DV = 'Mean Width/Depth')
           ) %>% 
  select(-pri.fac, -lcl, -ucl, -df) %>% 
                        mutate(
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>%
                        mutate(across(is.numeric, round, 5)) %>% 
                        rename(IV = 'mgmt',
                               `EMM` = 'the.emmean',
                               `Standard Error` = 'SE',
                               `Lower 95% CL` = 'lower.CL',
                               `Upper 95% CL` = 'upper.CL')  %>% 
                        #filter(DV == 'Mean Bankfull Width') %>% 
                        mutate(across(EMM:`Upper 95% CL`, round, 3)) %>% 
                        #pivot_wider(names_from = DV, values_from = IV:MAP_UNIT_N) %>% 
                        group_by(DV) %>% 
                        
                        gt()  %>%
  tab_header(
    title = "Estimated Marginal Mean (EMM) Results",
    subtitle = 'results from weighted regressions only'
  ) %>%
  opt_align_table_header(align = 'left') %>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "forestgreen", alpha = 0.5)
    ),
    locations = gt::cells_body(
      rows = IV == 'Reference'
    )
  )%>%
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "orange", alpha = 0.5)
    ),
    locations = gt::cells_body(
      rows = IV == 'Managed'
    )
  )   %>%  gt::tab_style(
    style = list(
      cell_text( weight = "bold")
    ),
    locations = list(
      cells_column_labels(gt::everything())
    )
  )%>%  gt::tab_style(
    style = list(
      cell_text( weight = "normal")
    ),
    locations = list(
      cells_body(columns = 'IV')
    )
  ) %>%  gt::tab_style(
    style = list(
      cell_text(style = 'italic')
    ),
    locations = list(
      cells_group()
    )
  )%>% 
  tab_source_note(md("**Table 4.**")) %>% 
  tab_footnote(footnote = md('**EMM** = Estimated Marginal Mean'),
               locations = cells_column_labels('EMM')) %>%
  tab_footnote(footnote = md('**CL** = Confidence Limit'),
               locations = cells_column_labels(c(`Lower 95% CL`, `Upper 95% CL`))) 
  
  
m6
mgmt_diff_gg_area_wd %>% group_by(MAP_UNIT_N) %>% 
  mutate(mean_man = ifelse(mgmt=='Reference', the.emmean, NA)) %>% 
  summarise(diff = exp(lower.CL-mean_man))
```

Now explore covariates with emm.

```{r}
bf.rg <- ref_grid(mod_bf_filt, at = list(fac_taudem_17all_int = seq(10000, 163291, 16329.1)))

emm <- plot(bf.rg, by = 'mgmt') + custom_theme()

emm_gg <- as.data.frame(emm$data) %>% tibble()


p1 <- emm_gg %>% mutate(shed_area = ifelse(mgmt %in% 'Reference', fac_taudem_17all_int+4000, fac_taudem_17all_int-4000),
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  #geom_point(data = fish_stuff , aes(mean_bf, shed_areakm2, color = mgmt), size = 3, alpha = 0.2)+
  geom_errorbar(aes(the.emmean, fac_taudem_17all_int, color=mgmt,xmin = lower.CL, xmax = upper.CL),
  position = position_dodge2(width = 0.005, padding = 0.005), size = .75) + 
  custom_theme(font_size = 12) + labs(x = 'Predicted Mean Bankfull Width (m)', 
                        y = 'Flow Accumulated Area (30x30m res)',
                        color = "Group",
                        title = 'Comparing estimated means by Watershed Area (km<sup>2</sup>) (without high residuals)',
                        subtitle = 'Average annual precipitation is held constant at 1193 (mm)')  +
  geom_point(aes(the.emmean, shed_area), size = 1) +
  scale_y_continuous(labels = comma) + 
  facet_wrap(~MAP_UNIT_N)
p1 

df_pred <- data.frame(pred = predict(mod_bf_filt)) %>% mutate(pred_ex = exp(pred))
bf.rg <- ref_grid(mod_bf_filt, at = list(us_precip_1981_2010_cpg_all = seq(10000, 163291, 16329.1)))

emm <- plot(bf.rg, by = 'mgmt') + custom_theme()

emm_gg <- as.data.frame(emm$data) %>% tibble()


p1 <- emm_gg %>% mutate(shed_area = ifelse(mgmt %in% 'Reference', us_precip_1981_2010_cpg_all+4000, us_precip_1981_2010_cpg_all-4000),
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  #geom_point(data = fish_stuff , aes(mean_bf, shed_areakm2, color = mgmt), size = 3, alpha = 0.2)+
  geom_errorbar(aes(the.emmean, us_precip_1981_2010_cpg_all, color=mgmt,xmin = lower.CL, xmax = upper.CL),
  position = position_dodge2(width = 0.005, padding = 0.005), size = .75) + 
  custom_theme(font_size = 12) + labs(x = 'Predicted Mean Bankfull Width (m)', 
                        y = 'Flow Accumulated Area (30x30m res)',
                        color = "Group",
                        title = 'Comparing estimated means by Watershed Area (km<sup>2</sup>) (without high residuals)',
                        subtitle = 'Average annual precipitation is held constant at 1193 (mm)')  +
  geom_point(aes(the.emmean, shed_area), size = 1) +
  scale_y_continuous(labels = comma) + 
  facet_wrap(~MAP_UNIT_N)
p1 



ba.rg <- ref_grid(mod_ba_filt, at = list(fac_taudem_17all_int = seq(10000, 163291, 16329.1)))

emm <- plot(ba.rg, by = 'mgmt') + custom_theme()

emm_gg <- as.data.frame(emm$data) %>% tibble()


p1 <- emm_gg %>% mutate(shed_area = ifelse(mgmt %in% 'Reference', fac_taudem_17all_int+4000, fac_taudem_17all_int-4000),
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  #geom_point(data = fish_stuff , aes(mean_bf, shed_areakm2, color = mgmt), size = 3, alpha = 0.2)+
  geom_errorbar(aes(the.emmean, fac_taudem_17all_int, color=mgmt,xmin = lower.CL, xmax = upper.CL),
  position = position_dodge2(width = 0.005, padding = 0.005), size = .75) + 
  custom_theme(font_size = 12) + labs(x = 'Predicted Mean Bankfull Width (m)', 
                        y = 'Watershed Area km2',
                        color = "Group",
                        title = 'Comparing estimated means by Watershed Area (km<sup>2</sup>) (without high residuals)',
                        subtitle = 'Average Basin Elevation is held constant at 1674 (m)\nTWI-CPG at 669')  +
  geom_point(aes(the.emmean, shed_area), size = 1) +
  facet_wrap(~MAP_UNIT_N)
p1 



wd.rg <- ref_grid(mod_wd_filt, at = list(us_precip_1981_2010_cpg_all = seq(10000, 163291, 16329.1)))

emm <- plot(wd.rg, by = 'mgmt') + custom_theme()

emm_gg <- as.data.frame(emm$data) %>% tibble()

emm_gg %>% select(us_precip_1981_2010_cpg_all)
p1 <- emm_gg %>% mutate(shed_area = ifelse(mgmt %in% 'Reference', us_precip_1981_2010_cpg_all+4000, us_precip_1981_2010_cpg_all-4000),
                        the.emmean = exp(the.emmean),
                        lower.CL = exp(lower.CL),
                        upper.CL = exp(upper.CL)) %>% filter(the.emmean >0) %>% 
  ggplot() +
  #geom_point(data = fish_stuff , aes(mean_bf, shed_areakm2, color = mgmt), size = 3, alpha = 0.2)+
  geom_errorbar(aes(the.emmean, us_precip_1981_2010_cpg_all, color=mgmt,xmin = lower.CL, xmax = upper.CL),
  position = position_dodge2(width = 0.005, padding = 0.005), size = .75) + 
  custom_theme(font_size = 12) + labs(x = 'Predicted Mean Bankfull Width (m)', 
                        y = 'Watershed Area km2',
                        color = "Group",
                        title = 'Comparing estimated means by Watershed Area (km<sup>2</sup>) (without high residuals)',
                        subtitle = 'Average Basin Elevation is held constant at 1674 (m)\nTWI-CPG at 669')  +
  geom_point(aes(the.emmean, shed_area), size = 1) +
  facet_wrap(~MAP_UNIT_N)
p1 

```

